Modal Abstractions for Virtualizing Memory Addresses

### 2025-07-17 background.tex
+

\begin{figure}
%    \begin{framed}
\begin{multicols}{2}
%\column{.59\textwidth}    
    \begin{figure}
%        \centering
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-0.5,xscale=0.5]
%uncomment if require: \path (0,471); %set diagram left start at 0, and has height of 471

@@

\end{tikzpicture}
          \caption{Accessing to the Page Referenced by L1 Entry}
        \label{fig:enter-label}
    \end{figure}
\columnbreak
    \begin{figure}
\begin{lstlisting}%[style=CStyleNum, basicstyle=\tiny]
static pte_t *pte_nxt_table (pte_t *entry){
 pte_t *next;
 // If not already present, try to allocate
 if (!entry->present){
  if (!pte_alloc(&next)) {
   return NULL;
  }
  entry->pfn = PTE_PFN((uintptr_t) next);
  entry->present = 1;
  } else {
   uintptr_t next_phys_addr = PTE_PFN_TO_ADDR(entry->pfn);        
   uintptr_t next_virt_addr = (uintptr_t) P2V(next_phys_addr);
   next = (pte_t *) next_virt_addr;
  }
  return next;
}   
pte_t *walkpgdir(pte_t *l4, void *va){ 
 pte_t *l4_entry = &l4[L4I(va)];
 pte_t *l3 = pte_nxt_table(l4_entry);
 pte_t *l3_entry = &l3[L3I(va)];
 pte_t *l2 = pte_nxt_table(l3_entry);
 pte_t *l2_entry = &l2[L2I(va)];  
 pte_t *l1 = pte_nxt_table(l2_entry);
 pte_t *l1_entry = &l1[L1I(va)];  
 return l1_entry
}
\end{lstlisting}
%          \caption{Walking page-table tree to locate L1 entry C-source code.}
%        \label{fig:enter-label}
    \end{figure}
\end{multicols}
%\end{framed}
    \vspace{-2.5em}
    \caption{x86-64 page table lookups.}
    \label{fig:pagetables}
    \vspace{-1em}
\end{figure}

>>>>

\begin{figure}
%    \begin{framed}
%\column{.59\textwidth}    
    \begin{subfigure}
%        \centering
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-0.5,xscale=0.5]
%uncomment if require: \path (0,471); %set diagram left start at 0, and has height of 471

@@

\end{tikzpicture}
          \caption{Accessing to the Page Referenced by L1 Entry}
        \label{fig:enter-label}
    \end{subfigure}
    \vfill
    \begin{multicols}{2}
%    \begin{figure}
\begin{lstlisting}%[style=CStyleNum, basicstyle=\tiny]
static pte_t *pte_nxt_table (pte_t *entry){
 pte_t *next;
 // If not already present, try to allocate
 if (!entry->present){
  if (!pte_alloc(&next)) {
   return NULL;
  }
  entry->pfn = PTE_PFN((uintptr_t) next);
  entry->present = 1;
  } else {
   uintptr_t next_phys_addr = PTE_PFN_TO_ADDR(entry->pfn);        
   uintptr_t next_virt_addr = (uintptr_t) P2V(next_phys_addr);
   next = (pte_t *) next_virt_addr;
  }
  return next;
}
\end{lstlisting}
\columnbreak
\begin{lstlisting}
pte_t *walkpgdir(pte_t *l4, void *va){ 
 pte_t *l4_entry = &l4[L4I(va)];
 pte_t *l3 = pte_nxt_table(l4_entry);
 pte_t *l3_entry = &l3[L3I(va)];
 pte_t *l2 = pte_nxt_table(l3_entry);
 pte_t *l2_entry = &l2[L2I(va)];  
 pte_t *l1 = pte_nxt_table(l2_entry);
 pte_t *l1_entry = &l1[L1I(va)];  
 return l1_entry
}
\end{lstlisting}
%          \caption{Walking page-table tree to locate L1 entry C-source code.}
%        \label{fig:enter-label}
 %   \end{figure}
\end{multicols}
%\end{framed}
    \vspace{-2.5em}
    \caption{x86-64 page table lookups.}
    \label{fig:pagetables}
    \vspace{-1em}
\end{figure}
